Species motif participation provides unique information about species risk of extinction

### 2022-06-16 manuscript/response_PRSB_round2.tex

        \them
        Line 247-254: This would all be greatly enhanced if there were some error bars on the figures.

        \us We have added error bars representing 95\% confidence intervals to this figure.

        \them
        Line 259-262: This result seems odd to me. Is this just because all of the potential apparent competition interactions are filled first, and really is more of an artefact of the constraints about the types of motifs that are possible within these networks? And perhaps the connectances being explored are unrealistic given these constraints?

        \us While we do not use a generative model that fills some motifs/interactions before others, we do not see any particular reason why apparent competition motifs should be filled first. More likely, the high frequencies of apparent competition reflects the tendency for resources to outnumber consumers, creating the classic ``pyramid shape'' food web. We can confirm, however, that the connectances we explore are realistic. We compare the structure of our simulated networks to the largest set of high-quality, similarly-sized empirical networks we could find. These networks had 50-77 species and connectances of 0.024-0.089, squarely within the range we simulate. We also, per the Associate Editor's request, compare the motif profiles and motif participation of these empirical webs to our simulated webs. We hope that this comparison will demonstrate the realism of our simulated networks.

### 2022-06-16 manuscript/supplement_motifs.tex

        Although previous work has shown that the niche model replicates the motif structure of empirical networks~\citep{Stouffer2005a,Stouffer2006}, we provide a comparison of the motif profiles and consumer motif participation for our simulated networks and the highest-quality empirical networks we could find within the same size range.
        For this comparison, we obtained all networks containing 50-100 species from \citet{globalwebdb}.
        These webs ranged in connectance from 0.024-0.089
        We then removed networks where sets of predators and prey were completely different (i.e., bipartite networks) or links were not clear (i.e., +/- effects rather than predation specifically).
        This yielded five vertebrate-dominated food webs describing the California coast in different years, four invertebrate-dominated food webs describing mainland US streams, 23 invertebrate-dominated food webs describing New Zealand streams, and five other invertebrate-dominated food webs.
        This final set of webs had 50-77 species and connectances of 0.2-0.21 - the upper range of connectance in our simulations.
        This may be partly due to relatively poor resolution of basal resources in these empirical webs: aggregation of many taxa into nodes such as `phytoplankton' will tend to decrease the number of species but leave the number of links unchanged, raising connectance.
        We note that most of these webs were compiled by just three research groups.
        Moreover, many of the webs are repeated samples of the same site  or closely-grouped sites.
        This means that these empirical networks cannot be considered fully independent samples.

>>>>

        Although previous work has shown that the niche model replicates the motif structure of empirical networks~\citep{Stouffer2005a,Stouffer2006}, we additionally provide a comparison of the motif profiles and consumer motif participation for our simulated networks and the highest-quality empirical networks we could find within the same size range.
        For this comparison, we obtained all networks containing 50-100 species from \citet{globalwebdb}.
        These webs ranged in connectance from 0.024-0.089.
        We then removed networks where sets of predators and prey were completely different (i.e., bipartite networks) or links were not clear (i.e., +/- effects rather than predation specifically).
        This yielded five vertebrate-dominated food webs describing the California coast in different years, four invertebrate-dominated food webs describing mainland US streams, 23 invertebrate-dominated food webs describing New Zealand streams, and five other invertebrate-dominated food webs.
        This final set of webs had 50-77 species and connectances of 0.2-0.21 - the upper range of connectance in our simulations.
        This may be partly due to relatively poor resolution of basal resources in these empirical webs: aggregation of many taxa into nodes such as `phytoplankton' will tend to decrease the number of species but leave the number of links unchanged, raising connectance.
        We note that most of these webs were compiled by just three research groups.
        Moreover, many of the webs are repeated samples of the same site  or closely-grouped sites.
        This means that these empirical networks cannot be considered fully independent samples.
